---
title: "Appendices"
author: "Hannah Connell"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r packages, include = FALSE}
# Load any packages you may need here
library(car)
library(ggplot2)
library(gridExtra) # can use if you want to create side-by-side plots (like in Figure 5)
```


```{r readData, include = FALSE}
combine <- read.csv("combine_defensive.csv", stringsAsFactors = TRUE)
```


***

#### Figure 1: Summary Ouput - Initial Model

```{r figure1, echo = FALSE}
lm_combine_initial <- lm(fortyyd ~  heightinchestotal + weight + position + vertical, data = combine)
summary(lm_combine_initial)
```

***

#### Figure 2: Residuals Plot - Initial Model

```{r figure2, echo = FALSE}
plot(lm_combine_initial, which = 1)
```

***

#### Figure 3: QQ Plot of Residuals - Initial Model

```{r figure3, echo = FALSE}
plot(lm_combine_initial, which = 2)
```

***

#### Figure 4: Scatterplot of Forty Yard Dash Times by Weight 

```{r figure4, echo = FALSE}
ggplot(data = combine, aes(x = weight, y = fortyyd)) + 
  
  geom_point(aes(color = position, shape = position)) + 
  
  
  labs(title = "Scatterplot of Forty Yard Dash Times vs Player Weight",
       x = "Weight (in lbs)",
       y = "Forty Yard Dash Time (in seconds)")
```

***

#### Figure 5: An Updated Version of the Model With Position as an Interaction Variable for Weight

```{r figure5, echo = FALSE}
lm_combine_updated <- lm(fortyyd ~  heightinchestotal + weight * position + vertical, data = combine)
summary(lm_combine_updated)
```

***

#### Figure 6: Scatterplot Matrix Including Twenty Yard Shuttle

```{r figure6, echo = FALSE}
plot( ~ fortyyd + heightinchestotal + weight + vertical + twentyss, data = combine)
```

***

#### Figure 7: Updated Model Including Twenty Yard Shuttle

```{r figure7, echo = FALSE}
lm_combine_updated2 <- lm(fortyyd ~  heightinchestotal + weight + position + vertical + twentyss, data = combine)
summary(lm_combine_updated2)
```

***

#### Figure 8: Scatterplot of Forty Yard Dash Times vs Twenty Yard Shuttle Times

```{r figure8, echo = FALSE}
ggplot(data = combine, aes(x = twentyss, y = fortyyd)) + 
  
  geom_point(aes(color = position, shape = position)) + 
  
  
  labs(title = "Scatterplot of Forty Yard Dash Times vs Twenty Yard Shuttle Times",
       x = "Twenty Yard Shuttle Time (in seconds)",
       y = "Forty Yard Dash Time (in seconds)")
```

***

#### Figure 9: Updated Model with an Interaction Between Twenty Yard Shuttle and Position

```{r figure9, echo = FALSE}
lm_combine_final <- lm(fortyyd ~  heightinchestotal + weight + vertical + twentyss * position, data = combine)
summary(lm_combine_final)
```

***

#### Figure 10: Final Model - CMF

$E(Y_{fortyyd}|X) = \beta_0 + \beta_1 X_{heightinchestotal} + \beta_2 X_{weight} + \beta_3 X_{vertical} + \beta_4 X_{twentyss} + \beta_5 I_{positionDE} + \beta_6 I_{positionDT} + \beta_7 I_{positionOLB} + \beta_8 I_{positionDE}X_{twentyss} + \beta_9 I_{positionDT}X_{twentyss} + \beta_{10} I_{positionOLB}X_{twentyss}$

***

#### Figure 11: Residuals Plot - Final Model

```{r figure11}

plot(lm_combine_final, which = 1)

```

***

#### Figure 12: QQ Plot of Residuals - Final Model

```{r figure12}

plot(lm_combine_final, which = 2)

```

***

#### Figure 13: Summary of Forty Yard Dash Times


```{r figure13, echo = FALSE}
summary(combine$fortyyd)
```

***

#### Figure 14: VIFs for Each Predictor 

```{r figure14, echo = FALSE}
vif(lm(fortyyd ~  heightinchestotal + weight + vertical + twentyss, data = combine))


```